Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-22 Methods-and-Results.Rmd
paragraph test

\subsubsubsection{Intergroup Contact} 
To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}”

>>>>

\paragraph{Intergroup Contact} 
To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}”

\paragraph{Intergroup Contact} To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}”
